Conversas Hiperligadas: Novo Paradigma de Comunicação e Colaboração, potenciado pela Tecnologia WebRTC

### 2015-04-11 tese/section01.tex
[ADD] review of NAT section

Initially \ac{NAT} offered an alternative for address exhaustion and a false sensation of better security, asymmetric \ac{NAT} became a vulgar configuration on the web. As a direct result, problems started to appear, the amount of ports that \ac{IP} disponibilizes is also small compared to our current needs, worse than that, \ac{NAT} also difficult end-to-end communication, forcing most of applications that follows this model to be implemented ineffectively.

@@

@@

On the other hand, \ac{TURN} uses public servers to redirect traffic between private endpoints, it may use a P2P network relay to find the best peer but, after that, the behavior is much like client-server. Direct communication is only achieved by \ac{STUN} when \ac{NAT} is a type \textit{full cone}. {\color{red} [reference to \ac{NAT} types]}. \ac{ICE} uses \ac{STUN} when it's possible and \ac{TURN} otherwise.

>>>>

Initially \ac{NAT} offered an alternative for address exhaustion and a minimal sensation of security. There are four types of \ac{NAT}, "Full Cone NAT", "Restricted Cone NAT", "Port Restricted Cone NAT", "Symmetric NAT".

Full Cone \ac{NAT} maps public each \ac{IP} address and port to a private \ac{IP} address and port, any external host can communicate with private hosts throught their mapped public address and port. This represents the least restrictive type of \ac{NAT} and as we will later, the unique type of \ac{NAT} that enables real time communications from point to point.

Restricted Cone \ac{NAT} requires that a private client must first send a message to an external host before it can receive messages from the same host. With this type of \ac{NAT}, the private client can be contacted from any port of the same external host.

Port Restricted Cone \ac{NAT} works in the same way as Restricted Cone \ac{NAT} but only allows communications from the same external host's IP address and port, ignoring all messages from other applications within the same external host.

Symmetric NAT maps different ports for each connection, as we will see later, this represents a problem on real time communications.

Asymmetric \ac{NAT} became a vulgar configuration on the web. As a direct result, problems started to appear, the amount of ports that \ac{IP} disponibilizes is also small compared to our current needs, worse than that, \ac{NAT} also difficult end-to-end communication, forcing most of applications that follows this model to be implemented ineffectively.

@@

\ac{STUN} servers are quite simple, they receive requests from \ac{NAT}ed clients, the source address of a request is the public address that \ac{NAT} mapped to the client, \ac{STUN} servers will reply the mapped public address to the client, so it knows its public \ac{IP} address and port. Because Symmetric \ac{NAT} changes \ac{IP} port for each different connection, \ac{STUN} servers will reply the \ac{IP} address and port of their connection, which will be useless to clients connections, that's why Symmetric \ac{NAT} represents a problem for real time communications.

On the other hand, \ac{TURN} uses public servers to redirect traffic between private endpoints, it may use a P2P network relay to find the best peer but, after that, the behavior is much like client-server. Direct communication is only achieved by \ac{STUN} when \ac{NAT} is a type \textit{full cone}. \ac{ICE} uses \ac{STUN} when it's possible and \ac{TURN} otherwise.

@@
